### 2020-02-21 manuscript/ERL_global_C_review.Rmd
Table 1 & Fig.2
added C cycle variables with no data to Table 1
started adding C cycle diagrams

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("tables_figures/C_variables.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE, caption = "Table 1. ForC variables included in this analysis. Shown are variable names and descriptions, the associated variable name(s) in the database, and number of plots with records. Complete list of variables with full definitions is available at [GitHub url].", escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12)  %>%
  pack_rows("Annual fluxes", 1, 21, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Stocks", 22, 32, latex_gap_space = "1em", colnum = 1, hline_before = FALSE)
```

@@

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("tables_figures/C_variables.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE, caption = "Table 1. ForC variables included in this analysis. Shown are variable names and descriptions, the associated variable name(s) in the database, and number of plots with records. Complete list of variables with full definitions is available at [GitHub url].", escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12)  %>%
  pack_rows("Annual fluxes", 1, 23, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Stocks", 24, 34, latex_gap_space = "1em", colnum = 1, hline_before = FALSE)
```

@@

![**Fig. 2 | C cycle diagram for mature tropical broadleaf forests.** Presented are mean±std, where geographically distinct areas are treated as the unit of replication. All units are Mg C ha-1 yr-1 (fluxes) or Mg C ha-1 (stocks). Arrows indicate fluxes, boxes indicate stocks. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.](tables_figures/Tropical broadleaf MATURE.png)
